|

### 2020-05-29 paper/Manuscript.Rmd
Update description and author note
Update authors in paper

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    affiliation: "3,4"
  - name: "Aaron Peikert"
    affiliation: "3,5"
  - name: "Barbara Vreede"
    affiliation: "6"
  - name: "Anna-Lena Lamprecht"
    affiliation: "2,7"
    email: "a.l.lamprecht@uu.nl"
  - name: "Loek Brinkman"
    affiliation: "2,8"
  - name: "Marijn E. Struiksma"
    affiliation: "2,9"
    email: "m.struiksma@uu.nl"

affiliation:
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2" 
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "Humboldt-Universitaet zu Berlin"
  - id: "6"
    institution: "University Library Utrecht"
  - id: "7"
    institution: "Utrecht University, Department of Information and Computing Sciences"
  - id: "8"
    institution: "UMC Utrecht"
  - id: "9"
    institution: "Utrecht University, Department of Language, Literature & Communication, Utrecht Institute of Linguistics OTS"

@@

authornote: |
  This is a preprint, not a peer-reviewed publication. Comments and
  contributions are welcome. Please contact the lead author.
  The lead author is supported by a NWO Veni grant (NWO grant number
  VI.Veni.191G.090).
  We acknowledge Jeroen Ooms for offering feedback and suggesting the use of the
  R package gert.
keywords          : "open science; reproducibility; r; dynamic document generation; version control, FAIR"
wordcount         : "8257"

>>>>

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    affiliation: "3,4"
  - name: "Loek Brinkman"
    affiliation: "2,5"
  - name: "Anna-Lena Lamprecht"
    affiliation: "2,6"
    email: "a.l.lamprecht@uu.nl"
  - name: "Aaron Peikert"
    affiliation: "3,7"
  - name: "Marijn E. Struiksma"
    affiliation: "2,8"
  - name: "Barbara Vreede"
    affiliation: "9"

affiliation:
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2"
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "University Medical Center Utrecht"
  - id: "6"
    institution: "Utrecht University, Department of Information and Computing Sciences"
  - id: "7"
    institution: "Humboldt-Universitaet zu Berlin"
  - id: "8"
    institution: "Utrecht Institute of Linguistics OTS"
  - id: "9"
    institution: "University Library Utrecht"

@@

authornote: |
  This is a preprint, not a peer-reviewed publication. Comments and
  contributions are welcome. Please contact the lead author.
  All authors of this paper, except the first, are listed in alphabetical order.
  Author contributions are detailed in the document 'authors.csv' on the project
  repository, at [https://github.com/cjvanlissa/worcs](https://github.com/cjvanlissa/worcs).
  The lead author is supported by a NWO Veni grant (NWO grant number
  VI.Veni.191G.090).
  We acknowledge Jeroen Ooms for offering feedback and suggesting the use of the
  R package gert.
keywords          : "open science; reproducibility; r; dynamic document generation; version control, FAIR"
wordcount         : "8257"
